\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
fixed missing closing } + added ICCUB affiliation
fixed affiliation

\author[a]{Carlos Garc\'{i}a-Garc\'{i}a}
\author[b]{David Alonso}
\author[b]{Emilio Bellini}

\affiliation[a]{Instituto de Física Fundamental, Consejo Superior de Investigaciones Científicas, c/. Serrano 123, E–28006, Madrid, Spain}
\affiliation[b]{Oxford Astrophysics, Department of Physics, Keble Road, Oxford, OX1 3RH, UK}

@@

    \subsection{Quantitative comparison}\label{ssec:results.quant}
      \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{./figures/run_sph_2b_NKA_TTTEEE_reldev_eigval_1stbin.pdf}
        \caption{Eigenvalues of the single-bin covariance matrices for all power spectra involving $\delta$ and $\gamma_E$. Results are shown for the sample covariance (solid blue), the NKA estimator (solid orange) and the spin-0 approximation (dashed green). The NKA and spin-0 estimators are able to recover the covariance eigenvalues with an accuracy $\lesssim5\%$.} \label{fig:eigv_1bin}
      \end{figure}
      \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{./figures/run_sph_2b_1stbin_chi2_TT_TE_EE.pdf}
        \caption{$\chi^2$ distributions for the cases without
          $\gamma_B$-modes. We compare the distributions obtained with the
          covariance matrix computed directly from the simulated power spectra
          (blue) and the two different analytical methods: NKA (orange) and
          spin-0 (green). In addition, the theoretical $\chi^2$ distribution
          has been included (dashed red). The distribution extracted from the
          simulation follows the theoretical expectation almost perfectly in
          all cases. In the cases of $\delta\times\gamma_E$ and
          $\gamma_E\times\gamma_E$ we observe small shifts in the peak
          $\chi^2$, of $\sim2$-$4\%$, while their width is recovered
          accurately (a difference $\lesssim 2\%$). We will show that these
          differences are due to the inaccuracy of the analytical
          approximations on the largest scales, and that they have a
          completely negligible impact on the final cosmological parameter
          constraints.} 
        \label{fig:chi2_1bin}
      \end{figure}
      \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{./figures/run_sph_2b_Spin0_NKA_TTTEEE_Full_chi2.pdf}
        \caption{Same as Figure \ref{fig:chi2_1bin} for the combination of all
          correlations between $\delta$ and $\gamma_E$ for two redshift bins,
          where similar conclusions hold. In this case, the distribution
          shift and width difference is less than a $3\%$ and $7\%$,
          respectively. 
        \label{fig:chi2_2bins}
      \end{figure}
      \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{./figures/contaminants_diag_cov.pdf}
        \caption{Diagonal of the covariance matrix estimated from simulations without contaminants (solid blue), with 200 contaminants deprojected (dashed orange) and the NKA estimator (solid green). The differences between the simulated cases are significantly smaller than those associated with the NKA estimator. The NKA method is therefore equally valid to approximate the covariance even in the presence of contaminant deprojection.}
        \label{fig:diag_conts}
      \end{figure}
      In order to quantify the validity of our analytical approximations, we need to compare the NKA covariance with the sample covariance estimated from the simulations. However, comparing two matrices is not as straightforward as comparing their matrix elements one by one. The covariance between far-away bandpowers is expected to be very close to zero, and therefore a direct comparison of those elements would easily yield large relative differences simply due to the statistical noise in the sample covariance matrix. We will therefore quantify the differences between the different covariances making use of scalar quantities formed from them. The impact of the analytical approximations on the final parameter constraints will then be described in detail in Section \ref{ssec:results.cosmo}.

>>>>

\author[a,b]{Carlos Garc\'{i}a-Garc\'{i}a}
\author[c]{David Alonso}
\author[c]{Emilio Bellini}

\affiliation[a]{Instituto de Física Fundamental, Consejo Superior de Investigaciones Científicas, c/. Serrano 123, E–28006, Madrid, Spain}
\affiliation[b]{Institut de Ci\`{e}ncies del Cosmos (UB–IEEC), c/. Martí i Franqués 1, E–08028, Barcelona, Spain}
\affiliation[c]{Oxford Astrophysics, Department of Physics, Keble Road, Oxford, OX1 3RH, UK}

@@

    \subsection{Quantitative comparison}\label{ssec:results.quant}
      \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{./figures/run_sph_2b_NKA_TTTEEE_reldev_eigval_1stbin.pdf}
        \caption{Eigenvalues of the single-bin covariance matrices for all power spectra involving $\delta$ and $\gamma_E$. Results are shown for the sample covariance (solid blue), the NKA estimator (solid orange) and the spin-0 approximation (dashed green). The NKA and spin-0 estimators are able to recover the covariance eigenvalues with an accuracy $\lesssim5\%$.} \label{fig:eigv_1bin}
      \end{figure}
      \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{./figures/run_sph_2b_1stbin_chi2_TT_TE_EE.pdf}
        \caption{$\chi^2$ distributions for the cases without
          $\gamma_B$-modes. We compare the distributions obtained with the
          covariance matrix computed directly from the simulated power spectra
          (blue) and the two different analytical methods: NKA (orange) and
          spin-0 (green). In addition, the theoretical $\chi^2$ distribution
          has been included (dashed red). The distribution extracted from the
          simulation follows the theoretical expectation almost perfectly in
          all cases. In the cases of $\delta\times\gamma_E$ and
          $\gamma_E\times\gamma_E$ we observe small shifts in the peak
          $\chi^2$, of $\sim2$-$4\%$, while their width is recovered
          accurately (a difference $\lesssim 2\%$). We will show that these
          differences are due to the inaccuracy of the analytical
          approximations on the largest scales, and that they have a
          completely negligible impact on the final cosmological parameter
          constraints.} 
        \label{fig:chi2_1bin}
      \end{figure}
      \begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{./figures/run_sph_2b_Spin0_NKA_TTTEEE_Full_chi2.pdf}
        \caption{Same as Figure \ref{fig:chi2_1bin} for the combination of all
          correlations between $\delta$ and $\gamma_E$ for two redshift bins,
          where similar conclusions hold. In this case, the distribution
          shift and width difference is less than a $3\%$ and $7\%$,
          respectively.}
        \label{fig:chi2_2bins}
      \end{figure}
      \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{./figures/contaminants_diag_cov.pdf}
        \caption{Diagonal of the covariance matrix estimated from simulations without contaminants (solid blue), with 200 contaminants deprojected (dashed orange) and the NKA estimator (solid green). The differences between the simulated cases are significantly smaller than those associated with the NKA estimator. The NKA method is therefore equally valid to approximate the covariance even in the presence of contaminant deprojection.}
        \label{fig:diag_conts}
      \end{figure}
      In order to quantify the validity of our analytical approximations, we need to compare the NKA covariance with the sample covariance estimated from the simulations. However, comparing two matrices is not as straightforward as comparing their matrix elements one by one. The covariance between far-away bandpowers is expected to be very close to zero, and therefore a direct comparison of those elements would easily yield large relative differences simply due to the statistical noise in the sample covariance matrix. We will therefore quantify the differences between the different covariances making use of scalar quantities formed from them. The impact of the analytical approximations on the final parameter constraints will then be described in detail in Section \ref{ssec:results.cosmo}.
